---
title: "Untitled"
author: "me"
date: "7/26/2020"
output:
  pdf_document: default
  html_document: default
---

```{r}
5+5
```

```{r}
library(zoo)
library(tseries)
library(FinTS)
library(rugarch)
LT_zoo_final<-read.zoo("L&T housing Finance.csv",header=TRUE,sep=",",format="%d-%b-%y",FUN = as.Date)
plot(LT_zoo_final[,5])

```


there is a trend in the closing  price hence i am taking the differnce and considering the log return.
```{r}
plot(LT_zoo_final[,13])
```
the return series seems to be constant at mean zero and volatility clustering is visible in graph


```{r}
ret_LT<-LT_zoo_final[-1,13]
dfts_LT<- ts(ret_LT,start=c(2010,1),end=c(2020,300),frequency = 365)
hist(dfts_LT)
```
the  return appears to be noormally distributed.
```{r}
shapiro.test(dfts_LT)
```
the series is staionary.

```{r}
mean(dfts_LT)
adf.test(ret_LT)
```
since p value is smaller than 0.05
hence we are rejecting the null hypothesis
hence the series is stationary. also the series is normal around mean 0.


```{r}
acf(dfts_LT)
acf(abs(dfts_LT))
acf(dfts_LT^2)
```
by acf function of return we can say there is no auto correlation and there will be no need of MA model also by looking at the acf of absolute  return  we can say that the large return are followed by large returns regardless of sign
MA(1) may be

```{r}
pacf(dfts_LT)
pacf(abs(dfts_LT))
pacf(dfts_LT^2)
```

there seems to be no need of any AR model to predict the log return series.
AR(1).

```{r}
Box.test(ret_LT,lag=12,type="Ljung")
```
```{r}
ArchTest(ret_LT)
```
since p value is less than 0.05 we are rejecting the null hypothesis and thus we can say there is arch effect in the series.


```{r}

arima001<-arima(ret_LT,order = c(0,0,1))
AIC(arima001)
"arima001"
arima010<-arima(ret_LT,order = c(0,1,0))
AIC(arima010)
"arima010"
arima100<-arima(ret_LT,order = c(1,0,0))
AIC(arima100);"arima100"
arima101<-arima(ret_LT,order = c(1,0,1))
AIC(arima101);"arima101"
arima110<-arima(ret_LT,order = c(1,1,0))
AIC(arima110);"arima110"
arima011<-arima(ret_LT,order = c(0,1,1))
AIC(arima011);"arima011"
arima111<-arima(ret_LT,order = c(1,1,1))
AIC(arima111);"arima111"
arima200<-arima(ret_LT,order = c(2,0,0))
AIC(arima200);"arima200"
arima210<-arima(ret_LT,order = c(2,1,0))
AIC(arima210);"arima210"
arima201<-arima(ret_LT,order = c(2,0,1))
AIC(arima201);"arima201"
arima211<-arima(ret_LT,order = c(2,1,1))

AIC(arima211);"arima211"
arima020<-arima(ret_LT,order = c(0,2,0))
AIC(arima020);"arima020"
arima120<-arima(ret_LT,order = c(1,2,0))
AIC(arima120);"arima120"
arima021<-arima(ret_LT,order = c(0,2,1))
AIC(arima021);"arima021"
arima121<-arima(ret_LT,order = c(1,2,1))
AIC(arima121);"arima121"
arima002<-arima(ret_LT,order = c(0,0,2))
AIC(arima002);"arima002"
arima102<-arima(ret_LT,order = c(1,0,2))    
AIC(arima102);"arima102"
arima012<-arima(ret_LT,order = c(0,1,2))
AIC(arima012);"arima012"
arima112<-arima(ret_LT,order = c(1,1,2))
AIC(arima112);"arima112"
arima222<-arima(ret_LT,order = c(2,2,2))
AIC(arima222);"arima222"
arima220<-arima(ret_LT,order = c(2,2,0))
AIC(arima220);"arima220"
arima202<-arima(ret_LT,order = c(2,0,2))
AIC(arima202);"arima202"
arima022<-arima(ret_LT,order = c(0,2,2))
AIC(arima022);"arima022"
arima212<-arima(ret_LT,order = c(2,1,2))
AIC(arima212);"arima212"
```
ARMA(1,0,1)<-(1,0,0)
is the best choice since there was not any reccomendation from acf and pacf function we will ignore these model for now .
```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,0)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```


```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(0,1)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```



```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,0)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```
```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(0,2)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```
```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,2)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```
```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,2)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,1)),mean.model =list(armaOrder=c(1,0,1)))
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```


```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(0,1)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,0)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```
```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```



```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,0)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```








```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(0,2)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```






```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,2)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```






```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(1,2)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```




```{r}
spec_of_garch_LT<- ugarchspec(variance.model = list(garchOrder=c(2,1)),mean.model =list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```




```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

this model is rejected since there is no leverage effect.






```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```


```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(1,2)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(2,1)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```



```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(2,2)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

sGARCH(0,2)   Akaike       -4.5795 sstd
sGARCH(2,0)   Akaike       -4.6343 sstd
sGARCH(2,1)   Akaike       -4.6599 sstd
sGARCH(2,2)   Akaike       -4.6650 sstd
sGARCH(1,1)   Akaike       -4.6611 sstd
sGARCH(1,2)   Akaike       -4.6657 sstd
gjrGARCH(2,1) Akaike       -4.6685 sstd
gjrGARCH(1,1) Akaike       -4.6703 sstd
gjrGARCH(1,2) Akaike       -4.6730 sstd
gjrGARCH(2,2)  Akaike      -4.6742 sstd



so we are taking (1,2) instead of (2,2) because many terme in it are not significant
```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(1,3)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(3,1)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(2,3)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```

```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(3,2)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```


```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(3,3)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT
```


going further is not leading any good results



```{r}
spec_of_garch_LT<-ugarchspec(variance.model =list(model="gjrGARCH",garchOrder=c(3,1)),mean.model = list(armaOrder=c(1,0,1)),distribution.model = "sstd")
my_model_LT<-ugarchfit(spec=spec_of_garch_LT,data=ret_LT,out.sample = 500)
my_model_LT

```



```{r}
back_testing<-ugarchroll(spec_of_garch_LT,ret_LT,n.ahead=1,n.start = 2000,refit.every  =30,refit.window ="moving",solver="hybrid",solver.control = list(trace=TRUE,tol= 1e-12,delta=1e-8),calculate.VaR = TRUE,VaR.alpha = c(0.01,0.05),keep.coef = TRUE)

```


```{r}
report(back_testing)
```

```{r}
forecast<- ugarchforecast(my_model_LT,data=ret_LT,out.sample = 500,n.ahead =100,n.roll = 100)
```


